Query Optimization for Dynamic Imputation

### 2017-03-02 paper/relatedwork.tex
paper: more tweaks
paper: add paragraph intro

\vspace{0.5in}
\subsection{Missing Values and Statistics}

@@

BayesDB~\cite{mansinghka2015bayesdb} provides users with a simple interface to 
leverage statistical inference techniques in a database. Non-experts
can use a simple declarative language (an extension of SQL), to specify models
which allow missing value imputation, amongst other broader functionality.
Experts can further customize strategies and express domain knowledge to
improve performance and accuracy.

>>>>

\subsection{Missing Values and Statistics}

@@

Other work has looked at integrating statistical models into databases.
For example, BayesDB~\cite{mansinghka2015bayesdb} provides users with a simple interface to leverage statistical inference techniques in a database. Non-experts
can use a simple declarative language (an extension of SQL), to specify models
which allow missing value imputation, amongst other broader functionality.
Experts can further customize strategies and express domain knowledge to
improve performance and accuracy.
